---
title: "Webscraping Project- Eagles95"
author: "Huma Meer and Rebecca Rogers"
date: "2022-07-30"
output: word_document
editor_options: 
  markdown: 
    wrap: 72
---

### Data Source:

The data used in this paper is [County Business Patterns
Data](https://www.census.gov/programs-surveys/cbp.html) extracted from
the Census Bureau website using an API and a census key. CBP is an annual series that provides subnational economic data by industry. This series includes the number of establishments, employment during the week of March 12 2020, first quarter payroll, and annual payroll. Since the data is collected at the county level, all variables used in our analysis are also presented at the county level for the year 2020.


### Data Exploration and Visualization: 

For our analysis, we worked on identifying the patterns in the business industries in the US as compared to the DMV metro area. We focused our analysis on the top paying industries by Average Annual Payroll per Employee (AP). We then further analyzed the nature of the business environment in the DMV area that would contribute to the disparities in the AP including which industries had the most establishments and which were the top employers. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(censusapi)
library(tigris)
```

```{r}
Sys.setenv(CENSUS_KEY="2af9f600486ef6ad342ed1e8a978c0956a70a52c")
readRenviron("~/.Renviron")
Sys.getenv("CENSUS_KEY")
```

### Calculating the Average Annual Payroll Per Employee by Industry for the DMV area

```{r}
cbp_dmv <- getCensus( name = "cbp" ,
           vintage = 2020,
           key = Sys.getenv("CENSUS_KEY"),
           vars = c("NAME","NAICS2017","NAICS2017_LABEL","PAYANN","EMP"),
          region = "state:11,24,51")

cbp_AP_dmv <- cbp_dmv %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumpayann= sum(PAYANN)) %>% 
  mutate(sumemp=sum(EMP)) %>% 
  mutate(annual_payroll_per_employee= sumpayann/sumemp) %>% 
  select(NAICS2017, NAICS2017_LABEL,annual_payroll_per_employee)

cbp_AP_dmv <- cbp_AP_dmv[!duplicated(cbp_AP_dmv), ]
cbp_AP_dmv$NAICS2017_LABEL[10] <- "Mgmt of Companies"
cbp_AP_dmv$NAICS2017_LABEL[9] <- "Scientific Services"
cbp_AP_dmv$NAICS2017_LABEL[2] <- "Mining, Quarrying"
cbp_AP_dmv$NAICS2017_LABEL[1] <- "Agriculture"
cbp_AP_dmv$NAICS2017_LABEL[8] <- "Real Estate"

```

### Creating a plot for Average Annual Payroll Per Employee by Industry for the DMV area

```{r}
dmv_api_plot <- data.frame(cbp_AP_dmv)%>% 
  slice_head(n=10) %>% 
  ggplot(aes(y =reorder(NAICS2017_LABEL, annual_payroll_per_employee), 
             x = annual_payroll_per_employee)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label=round(annual_payroll_per_employee, digits = 0)),   nudge_x = 5.5, nudge_y = -0.1,vjust=-0.1, size=3.5) +
  xlab("Annual Payroll per Employee ($1,000)") +
  labs(title ="Top 10 Instudries in DMV \n by Average Payroll per Employee") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
dmv_api_plot
```

### Creating a plot for Average Annual Payroll Per Employee by Industry for the US

```{r}
cbp_US <- getCensus( name = "cbp" ,
           vintage = 2020,
           key = Sys.getenv("CENSUS_KEY"),
           vars = c("NAME","NAICS2017","NAICS2017_LABEL","PAYANN","EMP"),
          region = "us")

cbp_AP_US <- cbp_US %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumpayann= sum(PAYANN)) %>% 
  mutate(sumemp=sum(EMP)) %>% 
  mutate(annual_payroll_per_employee= sumpayann/sumemp) %>% 
  select(NAICS2017_LABEL,annual_payroll_per_employee)

cbp_AP_US <- cbp_AP_US[!duplicated(cbp_AP_US), ]
view(cbp_AP_US)
cbp_AP_US$NAICS2017_LABEL[10] <- "Mgmt of Companies"
cbp_AP_US$NAICS2017_LABEL[9] <- "Scientific Services"
cbp_AP_US$NAICS2017_LABEL[2] <- "Mining, Quarrying"
cbp_AP_US$NAICS2017_LABEL[1] <- "Agriculture"
cbp_AP_US$NAICS2017_LABEL[8] <- "Real Estate"

US_AP_plot <- data.frame(cbp_AP_US)%>% 
  slice_head(n=10) %>% 
  ggplot(aes(y =reorder(NAICS2017_LABEL, annual_payroll_per_employee), x = annual_payroll_per_employee)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label=round(annual_payroll_per_employee, digits = 0)),
            nudge_x = 4.5, nudge_y = -0.1,
            vjust = 0) +
  xlab("Annual Payroll per Employee ($1,000)") +
  labs(title = "Top 10 Instudries in the US \n by Average Payroll per Employee") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
US_AP_plot

```

### Top 10 Employers in  DMV 

```{r}
cbp_EMP_dmv <- cbp_dmv %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumemp=sum(EMP)) %>%
  mutate(sumemp=(sumemp/1000)) %>% 
  select(NAICS2017, NAICS2017_LABEL, sumemp) %>% 
  arrange(desc(sumemp)) 
cbp_EMP_dmv <- cbp_EMP_dmv[!duplicated(cbp_EMP_dmv), ]
cbp_EMP_dmv2 <- cbp_EMP_dmv[1:10, ]
cbp_EMP_dmv2$industry <- c("Health care and social assistance",
                        "Professional, scientific services",
                        "Accommodation and food services",
                        "Waste Management", "Construction", 
                        "Other services",
                        "Finance and insurance", 
                        "Educational Services",
                        "Wholesale trade", "Information")
cbp_EMP_dmv2

DMV_EMP_plot <- data.frame(cbp_EMP_dmv2)%>% 
  ggplot(aes(y =reorder(industry, sumemp), x = sumemp)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label= round(sumemp, digits =0)), nudge_x = 60) +
  xlab("Total Employees (in 1000s)") +
  ggtitle("Top 10 Employers in DMV \n by Industry") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
DMV_EMP_plot
```

### Top 10 Employers in the US

```{r}
cbp_EMP_US <- cbp_US %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumemp=sum(EMP)) %>% 
    mutate(sumemp=(sumemp/1000)) %>% 
  select(NAICS2017, NAICS2017_LABEL, sumemp) %>% 
  arrange(desc(sumemp))
cbp_EMP_US <- cbp_EMP_US[!duplicated(cbp_EMP_US), ]
cbp_EMP_US2 <- cbp_EMP_US[1:10, ]
cbp_EMP_US2$industry <- c("Health care and social assistance",
                           "Accommodation, food services",
                           "Waste Management",
                           "Professional, scientific services", 
                           "Construction", 
                           "Finance and insurance",
                           "Wholesale trade", 
                           "Other services",
                           "Educational services", "Information")
cbp_EMP_US2

US_EMP_plot <- data.frame(cbp_EMP_US2)%>% 
  ggplot(aes(y =reorder(industry, sumemp), x = sumemp)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label= round(sumemp, digits =0)), nudge_x = 2000, nudge_y = -0.1) +
  xlab("Total Employees (in 1000s)") +
  ggtitle("Top 10 Employers in the US \n by Industry") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
US_EMP_plot
```

### Summary Plot for Industries with largest number of establishments in DMV 

```{r}
cbp_FIRM_dmv <- getCensus( name = "cbp" ,
                           vintage = 2020,
                           key = Sys.getenv("CENSUS_KEY"),
                           vars = c("NAME","STATE", "NAICS2017","NAICS2017_LABEL","EMP", "ESTAB"),
                           region = "state:11,24,51")
cbp_FIRM_dmv2 <- cbp_FIRM_dmv %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumestab=sum(ESTAB)) %>% 
  select(NAICS2017, NAICS2017_LABEL, sumestab) %>% 
  arrange(desc(sumestab)) 
cbp_FIRM_dmv2 <- cbp_FIRM_dmv2[!duplicated(cbp_FIRM_dmv2), ]
cbp_FIRM_dmv3 <- cbp_FIRM_dmv2[1:10, ]
cbp_FIRM_dmv3$NAICS2017_LABEL[6] <- "Waste Management"
cbp_FIRM_dmv3$NAICS2017_LABEL[1] <- "Professional, scientific services"
cbp_FIRM_dmv3$NAICS2017_LABEL[3] <- "Other Services"
DMV_FIRM_plot <- data.frame(cbp_FIRM_dmv3)%>% 
  ggplot(aes(y =reorder(NAICS2017_LABEL, sumestab), x = sumestab)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label= sumestab), nudge_x = 4000) +
  xlab("Total Number of Establishments") +
  ggtitle("Industries with the Most Establishments \n in DMV") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
DMV_FIRM_plot
```

### Firm Count by State in DMV Area

```{r}
cbp_FIRM_STATE_dmv <- cbp_FIRM_dmv %>% 
  as_tibble() %>% 
  group_by(NAME) %>% 
  mutate(sumestab=sum(ESTAB)) %>% 
  mutate(sumestab=sumestab/1000) %>% 
  select(NAME, sumestab) %>% 
  arrange(desc(sumestab)) 
cbp_FIRM_STATE_dmv <- cbp_FIRM_STATE_dmv[!duplicated(cbp_FIRM_STATE_dmv), ]
cbp_FIRM_STATE_dmv
DMV_FIRM_State_Plot <- cbp_FIRM_STATE_dmv %>% 
  ggplot(aes(y =reorder(NAME, sumestab), x = sumestab)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label= round(sumestab, digits=0)), nudge_x = 60) +
  xlab("Total Number of Firms (in 1000s)") +
  ggtitle("Total Establishments by State in the DMV Area") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
DMV_FIRM_State_Plot
```

### Summary Plot for Industry with largest number of Establishments in USA

```{r}
cbp_FIRM_us <- getCensus( name = "cbp" ,
                           vintage = 2020,
                           key = Sys.getenv("CENSUS_KEY"),
                           vars = c("NAME","STATE", "NAICS2017","NAICS2017_LABEL","EMP", "ESTAB"),
                           region = "us")
cbp_FIRM_us2 <- cbp_FIRM_us %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumestab=sum(ESTAB)) %>% 
  mutate(sumestab=(ESTAB/1000)) %>% 
  select(NAICS2017, NAICS2017_LABEL, sumestab) %>% 
  arrange(desc(sumestab)) 
cbp_FIRM_us2 <- cbp_FIRM_us2[!duplicated(cbp_FIRM_us2), ]
cbp_FIRM_us3 <- cbp_FIRM_us2[1:10, ]
cbp_FIRM_us3$NAICS2017_LABEL[8] <- "Waste Management"
cbp_FIRM_us3$NAICS2017_LABEL[1] <- "Professional, scientific services"
cbp_FIRM_us3$NAICS2017_LABEL[3] <- "Other Services"

US_FIRM_plot <- data.frame(cbp_FIRM_us3)%>% 
  ggplot(aes(y =reorder(NAICS2017_LABEL, sumestab), x = sumestab)) +
  geom_col(fill="#92C5DE")+
  geom_text(aes(label= round(sumestab, digits = 0)), nudge_x = 50) +
  xlab("Total Number of Firms (in 1000s)") +
  ggtitle("Industries with the Most Establishments \n in the US") +
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())
US_FIRM_plot

```

### Heat Map of DMV showing the number of establishments by County

```{r}

cbp_US_ESTAB <- getCensus( name = "cbp" ,
           vintage = 2019,
           key = Sys.getenv("CENSUS_KEY"),
           vars = c("NAME","ESTAB"),
            region = "county:*",
           regionin = "state:11,24,51")

options(tigris_use_cache = TRUE)
options(tigris_class = "sf")
DCMDVA<- counties(c("DC","MD","VA"))
DCMDVA_state <- states() %>% 
  filter(STATEFP %in% c("11","24","51"))

merged <-DCMDVA %>% 
  left_join(cbp_US_ESTAB, by=c("STATEFP"="state", "COUNTYFP"="county" ))


DC <- filter(DCMDVA_state, NAME == "District of Columbia") 
notDC <- filter(DCMDVA_state, NAME != "District of Columbia")

ggplot(data= merged)+
  geom_sf(aes(fill=ESTAB), color="white",size = 0.4)+
  geom_sf(data= DCMDVA_state,fill= NA, color="black")+
  geom_sf_label(data = DC,
    aes(label = STUSPS))+
  geom_sf_label(data = notDC,
    aes(label = STUSPS))+
  annotate(
   geom = "curve", x = -77.3, y = 39, xend = -80.1, yend = 39.5,
    curvature = -.3, arrow = arrow(length = unit(2, "mm"))
  )+
  annotate(
    geom = "text",
    x = -80.6,
    y = 39.7,
    size = 3,
    label = "Anne Arundel, MD",
    color = "red"
  )+
  theme(panel.grid.major = element_line(colour = "transparent"))+
  scale_fill_distiller(palette= "BuPu", direction = 1)+
  labs(title = "Number of Establishments by County", 
       caption = "Source: CBP")+
  labs(x = "", y = "")+
  theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank())
```

### Scatter Plot for Number of Employees and Average Payroll per Employee by Industry in DMV area

```{r}

DMV_EMP_AP <- cbp_EMP_dmv %>% 
  left_join(cbp_AP_dmv, by = "NAICS2017_LABEL")
DMV_EMP_AP <- DMV_EMP_AP[!duplicated(DMV_EMP_AP), ]
DMV_EMP_AP$labels <- c("Healthcare", "Professional Services",
                       "Accomodation & Food", "Waste Management",
                       "Construction", "Other Services",
                       "Finance & Insurance", "Education", "Wholesale",
                       "Information", "Management", "Art & Entertainment",
                       "Real Estate", "Utilities", "Minerals", "Agricultural",
                       "Not Classified")

DMV_EMP_AP_plot <- DMV_EMP_AP %>% 
  ggplot(aes(x = sumemp, y = annual_payroll_per_employee)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  geom_label(aes(label=labels), 
            nudge_x = 0.25, nudge_y = 0.25, 
            check_overlap = T,
            size = 3) +
  xlab("Total Employees") +
  ylab("Average Payroll Per Employee ($1,000)") +
  labs(main = "Total Employees and Average Payroll by Industry in DMV") +
  theme_minimal()
DMV_EMP_AP_plot
```
