---
title: "Grad Proj"
author: "Huma Meer"
date: '2022-07-23'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(censusapi)

```

```{r}
# Add key to .Renviron
Sys.setenv(CENSUS_KEY="2af9f600486ef6ad342ed1e8a978c0956a70a52c")
# Reload .Renviron
readRenviron("~/.Renviron")
# Check to see that the expected key is output in your R console
Sys.getenv("CENSUS_KEY")
```


```
Calculating the Average Annual Payroll Per Employeer by Industry for the DMV area only


cbp_dmv <- getCensus( name = "cbp" ,
           vintage = 2020,
           key = Sys.getenv("CENSUS_KEY"),
           vars = c("NAME","NAICS2017","NAICS2017_LABEL","PAYANN","EMP"),
          region = "state:11,24,51")

cbp_AP_dmv <- cbp_dmv %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumpayann= sum(PAYANN)) %>% 
  mutate(sumemp=sum(EMP)) %>% 
  mutate(annual_payroll_per_employee= sumpayann/sumemp) %>% 
  select(NAICS2017_LABEL,annual_payroll_per_employee)

cbp_AP_dmv <- cbp_AP_dmv[!duplicated(cbp_AP_dmv), ]
view(cbp_AP_dmv)

```

Creating a plot for dmv only
```{r}

data.frame(cbp_AP_dmv)%>% 
  slice_head(n=10) %>% 
  ggplot() +
  geom_col(aes(y =reorder(NAICS2017_LABEL, annual_payroll_per_employee), x = annual_payroll_per_employee))+
  theme_minimal()+
  theme(axis.title.y = element_blank())
  



```
FOR US

```{r}

cbp_US <- getCensus( name = "cbp" ,
           vintage = 2020,
           key = Sys.getenv("CENSUS_KEY"),
           vars = c("NAME","NAICS2017","NAICS2017_LABEL","PAYANN","EMP"),
          region = "us")

cbp_AP_US <- cbp_US %>% 
  as_tibble() %>% 
  filter(NAICS2017 %in% c("11","21","22","23","31","42","44","48","51","52","53","54","55","56","61","62","71","72", "81","99")) %>% 
  group_by(NAICS2017) %>% 
  mutate(sumpayann= sum(PAYANN)) %>% 
  mutate(sumemp=sum(EMP)) %>% 
  mutate(annual_payroll_per_employee= sumpayann/sumemp) %>% 
  select(NAICS2017_LABEL,annual_payroll_per_employee)

cbp_AP_US <- cbp_AP_US[!duplicated(cbp_AP_US), ]
view(cbp_AP_US)
  

data.frame(cbp_AP_US)%>% 
  slice_head(n=10) %>% 
  ggplot() +
  geom_col(aes(y =reorder(NAICS2017_LABEL, annual_payroll_per_employee), x = annual_payroll_per_employee))+
  theme_minimal()+
  theme(axis.title.y = element_blank())

